Emergency Homeless Shelter Availabilities Across Toronto

### 2024-09-26 paper/paper.qmd
added variable to simulated data + other minor changes

---
title: "Daily Shelter and Overnight Services Availabilities"
author: "Cher Ning-Li"
thanks: "Code and data are available at: https://github.com/cher-ning/shelter_occupancies"
date: today
date-format: long
abstract: "In this paper I analyze the capacity vs real occupancy of shelters across Canada."
#TODO Complete abstract after paper.
format: pdf
number-sections: true
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @citeTidyverse

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of occupancy rate of shelters across the months (@fig-occupancyrate-vs-month), from @opendatatoronto.

# check if occupancy rate varies over months
```{r}
#| label: fig-occupancyrate-vs-month
#| fig-cap: Shelter Occupancy Rate in 2024 Over the Months
#| echo: false

@@

@@

# Results

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

# Discussion

>>>>

---
title: "Emergency Homeless Shelter Availabilities Across Toronto"
author: "Cher Ning-Li"
thanks: "Code and data are available at: https://github.com/cher-ning/shelter_occupancies"
date: today
date-format: long
abstract: "In this paper I analyze the occupancy and capacity of emergency homeless shelters across Toronto."
#TODO Complete abstract after paper.
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Next, the @sec-data section will introduce the dataset used for the present analysis and the data cleaning methods applied. The following @sec-results will then go more into depth to discover trends and patterns in the data while @sec-discussion will connect these findings to current literature to understand the scope and urgency of the issues at hand.

# Data {#sec-data}
You can and should cross-reference sections and sub-sections. We use @citeR and @citeTidyverse

The dataset used for analysis is of occupancy rate of shelters in the year 2024 (@fig-occupancyrate-vs-month), from @opendatatoronto.

# check if occupancy rate varies over months
```{r}
#| label: fig-occupancyrate-vs-month
#| tbl-cap: Shelter Occupancy Rate in 2024 Over the Months
#| echo: false

@@

rate_means$month <- month.abb[rate_means$month]

@@

# Results {#sec-results}

@@

# Discussion {#sec-discussion}
